Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & QDR \\
\end{tabular}
}
\vspace{-2mm}
\caption{System configurations used for the experiments. \label{fig:systems}}
\vspace{-6mm}
\end{figure}

>>>>

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & 2x QDR \\
\end{tabular}
}
\vspace{-2mm}
\caption{System configurations used for the experiments. \label{fig:systems}}
\vspace{-6mm}
\end{figure}
